---
title: 'Feature Selection'
date: 2025-04-20
format: 
    html:
        embed-resources: true
---

## Target

16025 observations
unique row identifier: PATCODE + HOSPCODE

```{.r}
er_df |> distinct(PATCODE, HOSPCODE) |> nrow()
```

```{r}
dispostion_vars <- c("NODISP", "NOFU", "RETRNED", "RETREFFU", "LWBS", "LBTC", 
"LEFTAMA", "DOA", "DIEDED", "TRANNH", "TRANPSYC", "TRANOTH", 
"ADMITHOS", "OBSHOS", "OBSDIS", "OTHDISP")
```

| visit disposition       | count | description                                         |
|-----------|-------|-----------------------------------------------------|
| NODISP    | 0     | No answer to item                                   |
| NOFU      | 1202  | No follow-up planned                                |
| RETRNED   | 2062  | Return to ED                                        |
| RETREFFU  | 10824 | Return/Refer to physician/clinic for FU             |
| LWBS      | 327   | Left without being seen (LWBS)                      |
| LBTC      | 221   | Left before treatment complete (LBTC)               |
| LEFTAMA   | 228   | Left AMA (against medical advice)                   |
| DOA       | 9     | DOA (dead on arrival)                               |
| DIEDED    | 33    | Died in ED                                          |
| TRANNH    | 101   | Return/transfer to nursing home                     |
| TRANPSYC  | 150   | Transfer to psychiatric hospital                    |
| TRANOTH   | 206   | Transfer to non-psychiatric hospital                |
| ADMITHOS  | 2121  | Admit to this hospital                              |
| OBSHOS    | 177   | Admit to observation unit, then hospitalized        |
| OBSDIS    | 214   | Admit to observation unit, then discharged          |
| OTHDISP   | 310   | Other visit disposition                             |

**3** Broad Categories

## Features Overview

915 cols

#### Patient Demographics
```{r}
demographic <- c("AGER", "SEX", "ETHIM", "RACEUN", "RACERETH", "PAYTYPER")
```

#### Triage Variables

```{r}
triage <- c("VMONTH", "VDAYR", "WAITTIME", "LOV", "BPSYS", "BPDIAS", "PULSE", "RESPR", "PAINSCALE", "IMMEDR", "TEMPF")
```

#### Hospital Usage Variables

```{r}
hospital_usage <- c("ARREMS", "ARRTIME", "SEEN72")
```

```{r}
hosp_vars <- c("HOSPCODE", "PATCODE", "EMRED", "HHSMUE", 
"EHRINSE", "EDPRIM", "EDINFO", "OBSCLIN", "OBSSEP", "OBSPHYSED", 
"OBSHOSP", "OBSPHYSOT", "OBSPHYSUN", "BOARD", "BOARDHOS", "AMBDIV", 
"TOTHRDIVR", "REGDIV", "ADMDIV", "INCSHX", "INCPHYS", "EXPSPACE", 
"BEDREG", "KIOSELCHK", "CATRIAGE", "IMBED", "ADVTRIAG", "PHYSPRACTRIA", 
"FASTTRAK", "EDPTOR", "DASHBORD", "RFID", "WIRELESS", "ZONENURS", 
"POOLNURS", "SURGDAY", "BEDCZAR", "BEDDATA", "HLIST", "HLISTED", 
"EMEDRES", "REGION", "MSA")
```

#### Injury Variables

```{r}
injury <- c("INJURY", "INJURY72", "INTENT15", "INJURY_ENC", "CAUSE1", "CAUSE2", "CAUSE3")
```

#### Sample Weights

```{r}
wt_vars <- c("PATWT", "EDWT", "BOARDED")
```

#### Patient Chief Complaint Variables

Reason of Visit (specific/broad)
```{r}
reason_vars <- c("RFV1", "RFV2", "RFV3", "RFV4", 
"RFV5", "RFV13D", "RFV23D", "RFV33D", "RFV43D", "RFV53D")
```

#### Chronical

NOCHRON: yes/no/blank
TOTCHRON: numeric
else: binary

```{r}
chron_vars <- c("ETOHAB", "ALZHD", "ASTHMA", "CANCER", "CEBVD", "CKD", "COPD", 
"CHF", "CAD", "DEPRN", "DIABTYP1", "DIABTYP2", "DIABTYP0", "ESRD", 
"HPE", "EDHIV", "HYPLIPID", "HTN", "OBESITY", "OSA", "OSTPRSIS", 
"SUBSTAB", "NOCHRON")
```

#### Provider's Diagnosis

```{r}
diag_vars <- c("DIAG1", "DIAG2", "DIAG3", "DIAG4", 
"DIAG5", "PRDIAG1", "PRDIAG2", "PRDIAG3", "PRDIAG4", "PRDIAG5")
```

DIAGSCRN

TOTDIAG: numeric

```{r}
diag_test <- c("DIAGSCRN", "ABG", "BAC", "BMP", 
"BNP", "BUNCREAT", "CARDENZ", "CBC", "CMP", "BLOODCX", "TRTCX", 
"URINECX", "WOUNDCX", "OTHCX", "DDIMER", "ELECTROL", "GLUCOSE", 
"LACTATE", "LFT", "PTTINR", "OTHERBLD", "CARDMON", "EKG", "HIVTEST", 
"FLUTEST", "PREGTEST", "TOXSCREN", "URINE", "OTHRTEST", "ANYIMAGE", 
"XRAY", "CATSCAN", "CTCONTRAST", "CTAB", "CTCHEST", "CTHEAD", 
"CTOTHER", "CTUNK", "MRI", "MRICONTRAST", "ULTRASND", "OTHIMAGE", 
"COVIDTEST", "COVIDANTIBODY", "TOTDIAG")
```

#### Miscellaneous variables

```{r}
procedure_vars <- c("PROC", "BPAP", "BLADCATH", 
"CASTSPLINT", "CENTLINE", "CPR", "ENDOINT", "INCDRAIN", "IVFLUIDS", "LUMBAR", "NEBUTHER", "PELVIC", "SKINADH", "SUTURE", "OTHPROC", "TOTPROC")
```
```{r}
med_vars <- c("MED","NUMGIV", "NUMDIS", "NUMMED")
```
```{r}
vitals_after_triage <- c("VITALSD", "TEMPDF", 
"PULSED", "RESPRD", "BPSYSD", "BPDIASD")
```
```{r}
seen_vars <- c("NOPROVID", "ATTPHYS", 
"RESINT", "CONSULT", "RNLPN", "NURSEPR", "PHYSASST", "EMT", "MHPROV", 
"OTHPROV")
```

#### admitted to hosptial

Shouldn't be included

```{r}
admithos_vars <- c("ADMIT", "ADMTPHYS", 
"LOS", "HDDIAG1", "HDDIAG2", "HDDIAG3", "HDDIAG4", "HDDIAG5", 
"HDSTAT", "ADISP", "OBSSTAY", "STAY24")
```

```{r}

```

```{r}
length(demographic) + length(chron_vars) + length(diag_test) + length(hosp_vars) + length(hospital_usage) + length(injury) + length(med_vars) + length(procedure_vars) + length(reason_vars) + length(triage) + length(seen_vars) + length(diag_vars)
```